### 2019-11-07 report/paper.tex
Reformat section 2 so that it nicely aligns with its figure and fits on a single page.

% TODO: Does the image make sense here? It's not referenced within the Introduction.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/waldo_winter} 
    \caption{Exmaple of an image showing detections with \( (name, p, p_{ratio}) \) in red, ground truth in green}
    \label{fig:waldo-winter}
\end{figure}

\section{Proposed Solution}
Our proposed solution has two phases: pre-processing and detection.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/model_overview} 
    \caption{Schematic overview of the wlado / wenda / wizard detection pileline.}
    \label{fig:model-overview}
\end{figure}

In the pre-processing phase, we will take all the provided high-resolution training images and crop out the three characters using the given input bounding box annotations. Negative samples will be obtained by arbitiarily sampling regions from the images that do not overlap with the given character bounding boxes. We will scale all these images to a fixed size for simplification. We will then run k-means preprocessing on these images to map the colored sample images to grayscale values.

The details will be further discussed in \autoref{subsec:data-prep}\\

Our detection phase first involves histogramming two types of feature descriptors: gradients (HoG) and values (HoV).

HoG will be used to histogram horizontal and vertical gradients in the image, which could be quite helpful in identifying features like the horizontal stripes in Waldo and Wenda's shirts. HoV is to histogram values from a SIFT detector.

We will use our training samples to train support vector machines (SVM) as a classifier to determine whether a window is either \(Waldo, Wenda, Wizard or Negative\). The classifier will predict a probability \(p\) that a window belongs to a certain class, and a ratio \(p_ratio\) to indicate the classifier's confidence in ratio to the other classes.

Afterwhich, we will perform non-maximum supression to rermove overlapping windows by choosing the one with the highest probability in each group.

Finally, the resulting boxes with the class label will be drawn on the image with the value of its probability and ratio.

The details will be further discussed in \autoref{subsec:implementation}\\

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after kemans preprocessing (originally gray-scale, but color mapped for display purposes)}
    \label{fig:preprocessed-samples}
\end{figure}

@@

\vspace{0.5cm}
Generating negative samples is done by randomly sampling regions of differing scales and positions from the provided training images.
In this process we additionally make sure that none of the proposed negative samples overlap with any of the ground truth annotations present in the images.
Then we scale these proposed negative samples to \( (128 \times 128 ) \) px and apply the filtering described in the above paragraph to each sample.
Since the negative samples are randomly generated, we can create arbitrary amounts of them. 
For our testing \( \approx15000 \) worked well. 
Additonal information in the exact size of the dataset is shown in \autoref{tab:dataset-stats}

@@

>>>>

\section{Proposed Solution}
Our proposed solution has two phases: pre-processing and detection.\\

In the pre-processing phase, we will take all the provided high-resolution training images and crop out the three characters using
the given input bounding box annotations. Negative samples will be obtained by arbitiarily sampling
regions from the images that do not overlap with the given character bounding boxes. We will scale
all these images to a fixed size for simplification. We will then run k-means preprocessing on these
images to map the colored sample images to grayscale values. The details will be further discussed in
\autoref{subsec:data-prep}.\\

Our detection phase first involves histogramming two types of feature descriptors: gradients (HoG) and
values (HoV). HoG will be used to histogram horizontal and vertical gradients in the image, which could
be quite helpful in identifying features like the horizontal stripes in Waldo and Wenda's shirts. HoV is
to histogram values from a SIFT detector. We will use our training samples to train support vector
machines (SVM) as a classifier to determine whether a window is either \(Waldo, Wenda, Wizard or Negative\).
The classifier will predict a probability \(p\) that a window belongs to a certain class, and a ratio
\(p_{ratio}\) to indicate the classifier's confidence in ratio to the other classes.
In the next step, we will perform non-maximum supression to rermove overlapping windows by choosing the
one with the highest probability in each group. Finally, the resulting boxes with the class label will
be drawn on the image with the value of its probability and ratio as illustrated in
\autoref{fig:waldo-winter}. The details will be further discussed in \autoref{subsec:implementation}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.845\linewidth]{figures/waldo_winter} 
    \caption{Image showing detections with \( (name, p, p_{ratio}) \) in red, ground truth in green.}
    \label{fig:waldo-winter}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after k-means preprocessing (originally gray-scaled, but color mapped for display purposes).}
    \label{fig:preprocessed-samples}
\end{figure}

@@

\vspace{0.5cm}
Generating negative samples is done by randomly sampling regions of differing scales and positions from the provided training images.
In this process we additionally make sure that none of the proposed negative samples overlap with any of the ground truth annotations present in the images.
Then we scale these proposed negative samples to \( (128 \times 128 ) \) px and apply the filtering described in the above paragraph to each sample.
Since the negative samples are randomly generated, we can create arbitrary amounts of them. 
For our testing \( \approx15000 \) worked well. 
Additonal information in the exact size of the dataset is shown in \autoref{tab:dataset-stats}.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/model_overview} 
    \caption{Schematic overview of the Waldo / Wenda / Wizard detection pileline}
    \label{fig:model-overview}
\end{figure}
